---
title: "summarise_hai(): Summarising HAI data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{summarise_hai(): Summarising HAI data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
  fig.width = 7, fig.height = 4)
```

This vignette shows how to use`summarise_hai()` to total healthcare-associated infection (HAI) counts by infection type, age group, or sex.

```{r}
library(haiInsight)
data("hai_data_clean")
head(hai_data_clean)
```

## Totals by infection type (with kable feature)

```{r}
summarise_hai(hai_data_clean, by = "Infection_Type", as_kable = TRUE)
```

## Totals by age group

```{r}
summarise_hai(hai_data_clean)
```

## Totals by sex (with kable feature)

```{r}
summarise_hai(hai_data_clean, by = "Sex", as_kable = TRUE)
```

### Notes

- `hai_data_clean` is derived from the BHAI package’s German PPS 2011 data.

- Headline national estimates (cases, deaths, DALYs) are provided separately in `hai_headlines` for context, sourced from the published study.

## Learn More

For more ways to compare or extend your visualisations of HAI data,  
see the next vignette: **`summarising-hai`**.

<hr>
<div style="background:#f2f7ff; padding:12px; border-left:4px solid #4682b4; border-radius:6px; margin-top:20px;">
  <b>Next vignette:</b> Dive deeper into grouping and summarising results in 
  <code>summarising-hai</code>.
</div>

