---
title: "plot_hai_totals(): Visualising HAI totals"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plot_hai_totals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
  fig.width = 7, fig.height = 4)
```

This vignette demonstrates `plot_hai_totals()`, a quick wrapper around ggplot2 for bar charts of HAI totals by infection type, age group, or sex.

```{r}
library(haiInsight)
data("hai_data_clean")
head(hai_data_clean)
```

## By infection type

```{r, fig.alt="Bar chart showing total infections by infection type"}
plot_hai_totals(hai_data_clean, by = "Infection_Type")
```

## By age group

```{r, fig.alt="Bar chart showing total infections by age group"}
plot_hai_totals(hai_data_clean, by = "Age_Group")
```

## By sex

```{r, fig.alt="Bar chart showing total infections by sex"}
plot_hai_totals(hai_data_clean, by = "Sex")
```

## Learn More

For a deeper dive into summarising infection counts before plotting,  
see the companion vignette: **`summarising-hai`**.

<hr>
<div style="background:#f2f7ff; padding:12px; border-left:4px solid #4682b4; border-radius:6px; margin-top:20px;">
  <b>Next vignette:</b> Learn how to summarise totals before plotting in 
  <code>summarising-hai</code>.
</div>

